---
title: "Maps of electricity"
format: html
---

## Purpose

Make maps of the power stations to get across the point about the first stage.

## Planning

Need the power lines, the location of the stations, and the type of station. Then need the treated parishes.

```{r}
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("IBM Plex Mono", "ibm")
font_add_google("Roboto", "roboto")

showtext_opts(dpi = 300)
showtext_auto(enable = TRUE)
```


### Power lines

```{r}
library(tidyverse)
library(sf)

map_grid <- readRDS(here::here("maps", "elec_map_grid.rds"))

map_grid %>% 
  st_as_sf() %>% 
  filter(year == 1926) %>% 
  ggplot() +
  geom_sf()


```

### Counties

```{r}
counties <- st_read(here::here("data", "maps", "sweden_24_couties.shp"))

counties %>% 
  ggplot() +
  geom_sf()
```

```{r}
hydro <- tibble(
  name = c("Älvkarleby", "Olidan"),
  x = c(17.4489, 12.2727),
  y = c(60.5686, 58.2750)
)

hydro <- st_sf(st_sfc(st_point(c(17.4489, 60.5686)), st_point(c(12.2727, 58.2750))), crs = 4326) %>%
  mutate(name = case_when(
    row_number() == 1 ~ "Älvkarleby",
    TRUE ~ "Olidan"
  )) %>%
  rename(geometry = st_sfc.st_point.c.17.4489..60.5686....st_point.c.12.2727..58.275...) %>%
  st_transform(crs = 4326)
```

### Big power stations

```{r}

ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Fills
  scale_fill_manual(values = c("Treated parishes" = "#9C6114"), guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))) +
  scale_color_manual(
    values = c("Hydropower plants" = "#d7301f")
    # guide = guide_legend(override.aes = list(
    #   linetype = c("solid", "blank"),
    #   shape = c(NA, 18)
    # ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)

```

### Big power stations and power lines 1900

```{r}
ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1900"),
    data = map_grid %>%
      filter(year == 1900), linewidth = 1.5, alpha = .5, show.legend = "line"
  ) +
  # Fills
  scale_fill_manual(values = c("Treated parishes" = "#9C6114"), guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))) +
  scale_color_manual(
    values = c("Electricity lines\n1900" = "#000080", "Hydropower plants" = "#d7301f"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank"),
      shape = c(NA, 18)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1900.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```


### Big power stations and power lines 1911

```{r}
ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1911"),
    data = map_grid %>%
      filter(year == 1911), linewidth = 1.5, alpha = .5, show.legend = "line"
  ) +
  # Fills
  scale_fill_manual(values = c("Treated parishes" = "#9C6114"), guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))) +
  scale_color_manual(
    values = c("Electricity lines\n1911" = "#000080", "Hydropower plants" = "#d7301f"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank"),
      shape = c(NA, 18)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1911.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```

### Big power stations and power lines 1926

```{r}
ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .5, show.legend = "line"
  ) +
  # Fills
  scale_fill_manual(values = c("Treated parishes" = "#9C6114"), guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank"),
      shape = c(NA, 18)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```


### Big power stations and power lines 1926 and treated parishes

```{r}
parishes <- st_read(here::here("data", "maps", "Swedish_parishes_1926.shp"))

parishes <- parishes %>% 
  st_transform(4326)


treated_parishes <- readxl::read_excel(here::here("data", "first-stage", "parish-level-power-station-data-vf-copy.xlsx"))

treated_parishes <- treated_parishes %>% 
  select(ref_code, touching_treated.1, treated, distance_to_line)

parishes <- parishes %>% 
  inner_join(treated_parishes)

parishes %>% 
  ggplot(aes(fill = treated)) +
  geom_sf()

parishes_subset_treated <- parishes %>% 
  filter(treated == 1)

parishes_subset_control <- parishes %>% 
  filter(touching_treated.1 == 0,
         treated == 0,
         distance_to_line <= 250)

```


```{r}
ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated,  colour = "grey70", aes(fill = "Treated parishes")) + 
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  # Fills
  scale_fill_manual(values = c("Treated parishes" = "#fc8d59"), guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank"),
      shape = c(NA, 18)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_parishes.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```


### Big power stations and power lines 1926 and treated parishes and control parishes

```{r}
ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated,  colour = "grey70", aes(fill = "Treated parishes")) +
  # Control parishes
  geom_sf(data = parishes_subset_control,  colour = "grey70", aes(fill = "Control parishes")) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  # Fills
  scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank"),
      shape = c(NA, 18)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_and_control_parishes.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```

### Power stations and transformers

```{r}
df <- readxl::read_excel(here::here("data", "power-stations", "power-stations.xlsx"))

power_stations_sf <- df %>% 
  st_as_sf(coords = c("longitude", "latitude")) %>% 
  st_set_crs(4326)

power_stations_sf %>%
  # count(latitude, longitude, source_final) %>%
  ggplot() +
  geom_sf() +
  coord_sf() +
  facet_wrap(vars(source_final), nrow = 1)

power_stations_sf_transmitted <- power_stations_sf %>% 
  filter(source_final == "transmitted")

ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated,  colour = "grey70", aes(fill = "Treated parishes")) +
  # Control parishes
  geom_sf(data = parishes_subset_control, colour = "grey70", aes(fill = "Control parishes")) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  geom_sf(data = power_stations_sf_transmitted, aes(colour = "Transformers"), alpha = .7) +
  # Fills
  scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f", "Transformers" = "#1C9E77"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank", "blank"),
      shape = c(NA, 18, 16)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.75, 0.21),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_and_control_parishes_and_transformers.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```

### Power stations and water power

```{r}
power_stations_sf_water <- power_stations_sf %>% 
  filter(source_final == "water")

ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated, colour = "grey70", aes(fill = "Treated parishes")) +
  # Control parishes
  geom_sf(data = parishes_subset_control, colour = "grey70", aes(fill = "Control parishes")) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  geom_sf(data = power_stations_sf_water, aes(colour = "Hydropower plants\n(Incl. small scale)"), alpha = .7) +
  # Fills
  scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f", "Hydropower plants\n(Incl. small scale)" = "#E72A8A"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank", "blank"),
      shape = c(NA, 18, 16)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.75, 0.21),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_and_control_parishes_and_hydro.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```


### Power stations and steam

```{r}
power_stations_sf_steam <- power_stations_sf %>% 
  filter(source_final == "steam")

ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated,  colour = "grey70", aes(fill = "Treated parishes")) +
  # Control parishes
  geom_sf(data = parishes_subset_control,  colour = "grey70", aes(fill = "Control parishes")) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  geom_sf(data = power_stations_sf_steam, aes(colour = "Steam power plants"), alpha = .7) +
  # Fills
  scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f", "Steam power plants" = "#67A61F"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank", "blank"),
      shape = c(NA, 18, 16)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.75, 0.21),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_and_control_parishes_and_steam.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```


### Power stations and diesel

```{r}
power_stations_sf_diesel <- power_stations_sf %>% 
  filter(source_final == "diesel")

ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated, colour = "grey70", aes(fill = "Treated parishes")) +
  # Control parishes
  geom_sf(data = parishes_subset_control, colour = "grey70", aes(fill = "Control parishes")) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  geom_sf(data = power_stations_sf_steam, aes(colour = "Turbine generators\n(Diesel)"), alpha = .7) +
  # Fills
  scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f", "Turbine generators\n(Diesel)" = "#E6AB01"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank", "blank"),
      shape = c(NA, 18, 16)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.75, 0.21),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_and_control_parishes_and_diesel.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```
















```{r}
ggplot() +
  geom_sf(data = counties, colour = "grey70", fill = "#edf8fb") +
  # Power plants
  geom_point(aes(geometry = geometry, colour = "Hydropower plants"),
    stat = StatSfCoordinates,
    fun.geometry = sf::st_centroid,
    size = 10, shape = 18, alpha = .9,
    data = hydro
  ) +
  # Treated parishes
  geom_sf(data = parishes_subset_treated, aes(fill = "Treated parishes")) +
  # Control parishes
  geom_sf(data = parishes_subset_control, aes(fill = "Control parishes")) +
  geom_sf_text(aes(label = name), data = hydro, size = 8, nudge_y = .35) +
  # Lines
  geom_sf(aes(colour = "Electricity lines\n1926"),
    data = map_grid %>%
      filter(year == 1926), linewidth = 1.5, alpha = .3, show.legend = "line"
  ) +
  # Fills
  scale_fill_manual(
    values = c("Treated parishes" = "#fc8d59", "Control parishes" = "#fef0d9"),
    guide = guide_legend(override.aes = list(linetype = "blank", shape = NA))
  ) +
  scale_color_manual(
    values = c("Electricity lines\n1926" = "#000080", "Hydropower plants" = "#d7301f"),
    guide = guide_legend(override.aes = list(
      linetype = c("solid", "blank"),
      shape = c(NA, 18)
    ))
  ) +
  coord_sf(
    xlim = c(NA, 23),
    ylim = c(55.6, 65)
  ) +
  theme_void() +
  labs(
    x = NULL,
    y = NULL,
    fill = NULL,
    colour = NULL
  ) +
  theme(
    axis.text = element_blank(),
    panel.background = element_rect(fill = "#DCE9ED"),
    panel.grid = element_blank(),
    #
    legend.position = c(0.77, 0.11),
    text = element_text(family = "ibm", size = 15)
  )

ggsave(filename = here::here("maps/map_big_power_stations_line_1926_with_treated_and_control_parishes.jpeg"), device = "jpeg", width = 124, height = 196, units = "mm", dpi = 300)
```

