---
title: "Untitled"
format: html
---


```{r}
library(tidyverse)

df_unions <- read_csv("data/union-data/union_density_treatment_and_control.csv")

df_unions %>% select(parish_code, contains("FACK")) %>% 
pivot_longer(cols = contains("FACK"), names_to = "year", values_to = "FACK")  %>% 
mutate(year = parse_number(year)) %>% 
group_by(year) %>%
# count how many parishes have a value of zero for FACK by year
summarise(n = sum(FACK == 0)) 

1794 / 2027

1477 / 2027
```



First we want to check how many of the parishes have a value of zero for FACK in 1794 and 1477. We can do this by using the following code:
```{r}

df_unions %>% select(parish_code, treated, contains("FACK")) %>% 
pivot_longer(cols = contains("FACK"), names_to = "year", values_to = "FACK")  %>% 
mutate(year = parse_number(year)) %>% 
mutate(non_zero_flag = ifelse(FACK == 0, 0, 1)) %>%
group_by(year, treated) %>%
# count how many parishes have a value of zero for FACK by year
count(non_zero_flag) 





```



Now we want to calculate the percentage of parishes that have a zero value for each year by treatment status. We can do this by using the following code:


```{r}
df_unions %>% select(parish_code, treated, contains("FACK")) %>% 
pivot_longer(cols = contains("FACK"), names_to = "year", values_to = "FACK")  %>% 
mutate(year = parse_number(year)) %>% 
mutate(non_zero_flag = ifelse(FACK == 0, 0, 1)) %>%
group_by(year, treated) %>%
# count how many parishes have a value of zero for FACK by year
count(non_zero_flag)  %>% 
ungroup() %>%
group_by(year) %>%
mutate(percentage = n / sum(n)) 

```


Now we need to join this to the parishes that we have in the sample

```{r}
library(gt)



df_unions %>% 
filter(distance_to_line <= 300) %>% 
select(parish_code, treated, contains("FACK")) %>% 
pivot_longer(cols = contains("FACK"), names_to = "year", values_to = "FACK")  %>% 
mutate(year = parse_number(year))  %>% 
# filter(FACK != 0) %>% 
group_by(year, treated) %>%
summarise(mean_FACK = mean(FACK, na.rm = TRUE), n = n())  %>% 
mutate(treated = ifelse(treated == 1, "Treated", "Control")) %>%
gt()  %>% 
cols_label(n = "Number of parishes",
mean_FACK = "Mean union density",
treated = "Group") %>% 
fmt_number(columns = c(mean_FACK), decimals = 2)  %>% 
gtsave(here::here("figures", "union_density_treatment_and_control.png"))
```




```{r}
df_unions_joined <- readxl::read_excel(here::here("data", "parishes", "union_membership_and_treated_groups_merged.xlsx"), sheet = 2)

df_unions_joined %>% view()

df_unions_joined %>% filter(parish_code == "168601") %>% view()

parishes_we_have_info_for <- df_unions_joined %>%
filter(!is.na(population_1930)) %>% 
select(parish_code) %>%
distinct()


df_unions_joined_1930_info <- df_unions_joined %>% 
filter(parish_code %in% parishes_we_have_info_for$parish_code,
distance_to_line <= 300) %>% 
filter(type_of_organization == "FACKF") 


df_unions_joined_1930_info 

# Assuming your dataframe is df_unions_joined_1930_info

# Calculate the average for the 10 year window around 1900
df_unions_joined_1930_info$avg_1900 <- rowMeans(df_unions_joined_1930_info[,paste0("n_members_", 1895:1904)], na.rm = TRUE)

# Calculate the average for the 10 year window around 1910
df_unions_joined_1930_info$avg_1910 <- rowMeans(df_unions_joined_1930_info[,paste0("n_members_", 1905:1914)], na.rm = TRUE)

# Calculate the average for the 10 year window around 1930
df_unions_joined_1930_info$avg_1930 <- rowMeans(df_unions_joined_1930_info[,paste0("n_members_", 1925:1934)], na.rm = TRUE)

df_unions_joined_1930_info_sum <- df_unions_joined_1930_info %>%
  group_by(parish_code) %>%
  mutate(
    sum_avg_1900 = sum(avg_1900, na.rm = TRUE),
    sum_avg_1910 = sum(avg_1910, na.rm = TRUE),
    sum_avg_1930 = sum(avg_1930, na.rm = TRUE)
  ) %>% 
  ungroup() 




df_unions_joined_1930_info_sum_avgs <- df_unions_joined_1930_info_sum %>% 
select(parish_code, treated, contains("FACK"), contains("population"), contains("sum_avg"))  %>% 
mutate(density_1900 = sum_avg_1900 / population_1900,
density_1910 = sum_avg_1910 / population_1910,
density_1930 = sum_avg_1930 / population_1930)  %>% 
select(parish_code, treated, density_1900, density_1910, density_1930, contains("sum_avg_"), contains("population"))  %>% 
distinct()

df_unions_joined_1930_info_sum_avgs %>%
filter(parish_code == "168601") %>% view()

df_unions_joined_1930_info_sum_calcs <- df_unions_joined_1930_info_sum %>% 
select(parish_code, treated, contains("FACK"), contains("population"), contains("sum_avg"))  %>% 
mutate(density_1900 = sum_avg_1900 / population_1900,
density_1910 = sum_avg_1910 / population_1910,
density_1930 = sum_avg_1930 / population_1930)  %>% 
select(parish_code, treated, density_1900, density_1910, density_1930)  %>% distinct() %>% view()
group_by(treated) %>%
summarise(mean_density_1900 = mean(density_1900, na.rm = TRUE),
mean_density_1910 = mean(density_1910, na.rm = TRUE),
mean_density_1930 = mean(density_1930, na.rm = TRUE),
n = n())  %>% 
pivot_longer(cols = contains("density"), names_to = "year", values_to = "density")   %>% 
mutate(year = parse_number(year),
treated = ifelse(treated == 1, "Treated", "Control")) %>%
group_by(year) %>%
mutate(ratio = density / lag(density)) 


df_unions_joined_1930_info_sum_calcs %>% 
gt()   %>% 
cols_label(density = "Mean union density",
treated = "Group",
ratio = "Ratio of treated to control union density") %>%
fmt_number(columns = c(density), decimals = 3)  %>% 
fmt_number(columns = c(ratio), decimals = 2)  %>%
tab_header(title = md("**Union density by treatment status and year**"),
subtitle = md("Mean union density is calculated by averaging the number of union members in a 10 year window divided by population from census in year"))   %>% 
tab_style(
  style = cell_text(weight = "bold"),
  locations = cells_row_groups()
) %>% 
gtsave(here::here("figures", "union_density_treatment_and_control_by_year.png"))



```




Check for occupational groupings. 



```{r}
library(arrow)

df_census <- read_parquet("data/census/census_1930_excl_unbalanced_controls.parquet")


df_census %>%
filter(electricity_job_direct == 0, electricity_job_indirect == 0) %>%
count(napp_title, sort = T) %>% 
head(20) %>% 
gt()
```



Now we want to join parish level data on electrification to the union density data


```{r}
df_union_density = read_csv("data/union-data/union_density_treatment_and_control.csv") %>% 
select(parish_code, contains("FACK"))  %>% 
distinct()

df_union_density$popular_movement_density_1900_FACKF <- pmax(pmin(df_union_density$popular_movement_density_1900_FACKF, 100), 0)
df_union_density$popular_movement_density_1910_FACKF <- pmax(pmin(df_union_density$popular_movement_density_1910_FACKF, 100), 0)
df_union_density$popular_movement_density_1930_FACKF <- pmax(pmin(df_union_density$popular_movement_density_1930_FACKF, 100), 0)

df_first_stage = readxl::read_excel("data/first-stage/04_firststage-data.xlsx", sheet = 1)

df_first_stage <- df_first_stage %>% 
mutate(parish_code = str_remove(ref_code, "SE/"),
# now drop the last three characters and set it to a numeric
parish_code = as.numeric(str_sub(parish_code, 1, -4))) 


df_first_stage <- df_first_stage %>% 
left_join(df_union_density, by = "parish_code") 

library(haven)

df_first_stage %>% 
rename(union_density_1900 = popular_movement_density_1900_FACKF,
union_density_1910 = popular_movement_density_1910_FACKF,
union_density_1930 = popular_movement_density_1930_FACKF) %>%
select(!contains("touching")) %>% 
write_dta(here::here("data", "first-stage", "first_stage_data_with_union_density.dta"))
```








Starting again to join the union membership data up to the population data



```{r}
df_unions_joined <- readxl::read_excel(here::here("data", "parishes", "union_membership_and_treated_groups_merged.xlsx"), sheet = 2)

df_unions_joined
```