---
title: "Untitled"
format: html
---

Purpose

We need to match the population data for 1900 and 1910 to the union membership data. 

Because we have geom_id and ref code for these, would be ideal to match these up to the histmaps map.

```{r}
library(tidyverse)
library(histmaps)
library(ipumsr)
library(sf)

dat <- ipumsr::read_ipums_micro(
  ddi = "data/1900-1910-census/ipumsi_00008.xml",
  data_file = "data/1900-1910-census/ipumsi_00008.dat.gz"
)

dat %>% count(YEAR, sort = T)

dat %>% colnames()

dat_sample <- dat %>%
slice_sample(n = 1000)

dat_sample %>% write_csv("data/1900-1910-census/sample.csv")

parish_population_count <- dat %>% select(YEAR, PARSE) %>% count(YEAR, PARSE) %>% arrange(PARSE, YEAR)

parish_population_count %>% write_csv2("data/1900-1910-census/population_counts.csv")
```


```{r}
parish_population_count <- read_csv2("data/1900-1910-census/population_counts.csv") %>% janitor::clean_names() %>% rename(population = n,
parish_code = parse)

```

parish names from 1900 and 1910


```{r}
df_parish_names = readxl::read_excel("data/1900-1910-census/parish_codes_ipums.xlsx")

df_parish_names <- df_parish_names %>% 
separate_wider_delim(parish_code, delim = "           ", names = c("parish_code", "parish_name"))  %>% 
mutate(parish_code = parse_number(parish_code))


df_parish_names %>% filter(str_detect(parish_code, "158004"))

df_parish_names %>% filter(str_detect(parish_code, "248207"))

df_parish_names %>% filter(str_detect(parish_code, "188003"))

df_parish_names %>% filter(str_detect(parish_code, "58301"))

```

Join parish names to population

```{r}

parish_population_count_with_names <- parish_population_count %>% left_join(df_parish_names, by = c("parish_code"))
```


```{r}
parish_population_count_with_names
```

So what do I need to do here?

I need to join this data up to the 1930 parishes map, so that we can then join it to the union membership data.


```{r}
parish_map <- get_boundaries(1930, "parish")

parish_map_st <- st_as_sf(parish_map)

parish_map_st <- parish_map_st %>% 
st_transform(4326)

parish_map_st <- parish_map_st %>% 
mutate(parish_code = parse_number(str_remove(ref_code, "SE/"))) 

parish_map_st_to_join <- parish_map_st %>% select(geom_id, ref_code, name, parish_code) %>% as_tibble() %>% select(-geometry)

parish_map_st_to_join %>% 
anti_join(parish_population_count_with_names, by = c("parish_code" = "parish_code")) 



# parish_population_count_with_names %>% 
# anti_join(parish_map_st_to_join, by = c("parish_code" = "parish_code"))  %>% view()


parish_map_st_to_join %>% filter(str_detect(name, "Helsingborg"))


parish_population_count_with_names %>% filter(str_detect(parish_name, "Helsingborg"))

parish_population_count_with_names %>% filter(str_detect(parish_code, "178001"))
```


So the takeaway is that I need to shorten all the data sources to the same level of detail, the short code that drops the last three digits from the long parish code.


```{r}
parish_population_count_with_names_short <- parish_population_count_with_names %>%
    mutate( # create parish_code_short by dropping final 3 digits
        parish_code_short = str_sub(parish_code, end = -4),
        parish_code_short = as.numeric(parish_code_short)
    ) %>%
    group_by(year, parish_code_short) %>%
    mutate(total_population = sum(population)) %>% 
    ungroup()


parish_population_count_with_names_short <- parish_population_count_with_names_short %>% 
select(year, parish_code_short, total_population)  %>% distinct()

write_rds(parish_population_count_with_names_short, here::here("data", "union-data", "snd", "parish-population-by-parish-for-1930-check-v1.rds"))
```

Now do the same with the union membership data

```{r}
df_joined_long_fackf_distinct_no_zeros <- read_rds(here::here("data", "union-data", "snd", "union-membership-by-parish-v1.rds"))

df_joined_long_fackf_distinct_no_zeros_total <- df_joined_long_fackf_distinct_no_zeros %>% 
mutate( 
    parish_code = str_remove(ref_code, "SE/"),
    # create parish_code_short by dropping final 3 digits
    parish_code_short = str_sub(parish_code, end = -4),
    parish_code_short = as.numeric(parish_code_short)
)  %>% 
select(-parish_code)  %>% 
group_by(year, parish_code_short)  %>%
summarise(total_members_agg = sum(total_members, na.rm = T))  %>% 
ungroup() %>% 
mutate(total_members_agg = case_when(
    total_members_agg == 0 ~ NA_real_,
    TRUE ~ total_members_agg
)) %>% 
arrange(parish_code_short) 

df_joined_long_fackf_distinct_no_zeros_total
```


Get population for 1930


```{r}
library(arrow)
df_census_1930 <- read_parquet(here::here("data", "census", "census_1930.parquet"))

population_1930 <- df_census_1930 %>% count(ref_code_current_parish_x) %>% 
rename(parish_code_short = ref_code_current_parish_x,
total_population = n) %>%
mutate(year = 1930)

population_1930
```


Join this population data to the other data

```{r}
parish_population_count_with_names_short_and_1930 <- bind_rows(parish_population_count_with_names_short, population_1930) %>% 
arrange(parish_code_short, year) 

# parish_population_count_with_names_short_and_1930 %>% view()
```


Join the data together, and calculate the average for 1880, 1890, 1900, 1910, with a 5 year window.



```{r}
df_joined_long_fackf_distinct_no_zeros_total_window <- df_joined_long_fackf_distinct_no_zeros_total %>%
    mutate(window = case_when(
        between(year, 1875, 1885) ~ 1880,
        between(year, 1885, 1895) ~ 1890,
        between(year, 1895, 1905) ~ 1900,
        between(year, 1905, 1915) ~ 1910,
        between(year, 1915, 1925) ~ 1920,
        between(year, 1925, 1935) ~ 1930,
        TRUE ~ NA_real_
    )) %>%
    group_by(window, parish_code_short) %>%
    mutate(total_members_agg_window = round(mean(total_members_agg, na.rm = T))) %>%
    ungroup() %>%
    select(window, parish_code_short, total_members_agg_window) %>%
    distinct() %>%
    filter(!is.na(window)) %>%
    rename(year = window, total_members = total_members_agg_window)



df_union_density <- df_joined_long_fackf_distinct_no_zeros_total_window %>%
    left_join(parish_population_count_with_names_short_and_1930, by = c("year", "parish_code_short")) %>%
    mutate(union_density = total_members / total_population) %>%
    mutate(union_density = case_when(
        union_density > 1 ~ 0.5,
        TRUE ~ union_density
    ))


df_union_density %>% write_rds(here::here("data", "union-data", "snd", "union-density-by-parish-v1.rds"))


df_union_density_wide <- df_union_density %>%
    select(year, parish_code_short, union_density) %>%
    filter(year != 1920) %>%
    pivot_wider(names_from = year, values_from = union_density, names_prefix = "union_density_")


df_union_density_wide %>% skimr::skim()


parish_population_count_with_names %>% filter(str_detect(parish_code, "18021"))


```




Calculate for treated parishes

```{r}
df_union_density_wide

treated_parishes <- readxl::read_excel(here::here("data", "parishes", "treated_parishes_with_distance_threshold_and_population.xlsx"))


treated_parishes <- treated_parishes %>%
    mutate(
        parish_code_short = str_remove(parish_code, "SE/"),
        parish_code_short = str_sub(parish_code_short, end = -4),
        parish_code_short = as.numeric(parish_code_short)
    ) %>%
    group_by(parish_code_short) %>%
    slice(1) %>%
    ungroup()


treated_parishes_to_join <- treated_parishes %>% select(parish_code_short, distance_to_line, treated)

treated_parishes_to_join

df_union_density_wide_treated <- df_union_density_wide %>%
    left_join(treated_parishes_to_join, by = c("parish_code_short")) %>%
    mutate(treated = case_when(
        is.na(treated) ~ 0,
        TRUE ~ treated
    ))

df_union_density_wide_treated %>%
    write_rds(here::here("data", "union-data", "snd", "union-density-by-parish-wide-to-join-v0.rds"))


df_union_density_wide_treated %>%
    select(-c(union_density_1880, treated, distance_to_line)) %>%
    write_csv(here::here("data", "union-data", "snd", "union-density-by-parish-wide-to-join-v1.csv"))
```

Table for how many parishes we have information on

```{r}
df_union_density_wide_treated <- read_rds(here::here("data", "union-data", "snd", "union-density-by-parish-wide-to-join-v0.rds"))

n_non_nan <- df_union_density_wide_treated %>%
    filter(distance_to_line <= 300) %>%
    # across union_density columns, count how many times there is a value
    summarise(across(starts_with("union_density"), ~ sum(!is.na(.)))) %>%
    mutate(type = "non_nan")

n_nan <- df_union_density_wide_treated %>%
    filter(distance_to_line <= 300) %>%
    # across union_density columns, count how many times there is a value
    summarise(across(starts_with("union_density"), ~ sum(is.na(.)))) %>%
    mutate(type = "nan")

n_share_complete <- n_non_nan %>% bind_rows(n_nan)


n_share_complete_table <- n_share_complete %>%
    pivot_longer(cols = -type) %>%
    mutate(name = parse_number(name)) %>%
    pivot_wider(names_from = type, values_from = value) %>%
    mutate(share_complete = non_nan / (non_nan + nan)) %>%
    mutate(total = non_nan + nan) %>%
    rename(
        year = name,
        union_membership_data_present = non_nan,
        union_membership_data_missing = nan
    )

n_share_complete_table %>%
    write_csv(here::here("data", "union-data", "snd", "share-complete-union-density-summary.csv"))

n_share_complete_table %>%
    gt() %>%
    cols_label(year = "Year", union_membership_data_present = "Data Present", union_membership_data_missing = "Data Missing", share_complete = "Share Complete", total = "Total number of Parishes") %>%
    fmt_number(columns = c(union_membership_data_present, union_membership_data_missing, total), decimals = 0) %>%
    fmt_percent(columns = share_complete, decimals = 2) %>%
    tab_header(
        title = md("**Share of Parishes with Union Membership Data**"),
        subtitle = "In subset of parishes used in regression sample"
    ) %>%
    gtsave(here::here("figures", "091-tab-union-density-share-complete.png"))

```

```{r}
library(gt)

df_union_density_wide_tab <- df_union_density_wide_treated %>%
    filter(distance_to_line < 300) %>%
    group_by(treated) %>%
    summarise(across(starts_with("union_density"), mean, na.rm = T)) %>%
    pivot_longer(cols = -treated, names_to = "year", values_to = "union_density") %>%
    mutate(year = parse_number(year)) %>%
    mutate(treated = case_when(
        treated == 1 ~ "Treated",
        TRUE ~ "Control"
    ))


df_union_density_wide_tab %>%
    pivot_wider(names_from = treated, values_from = union_density) %>%
    gt() %>%
    fmt_percent(columns = c(Control, Treated), decimals = 2) %>%
    sub_missing(columns = c(Control, Treated), missing_text = "-") %>%
    cols_label(year = "Year") %>%
    tab_header(
        title = md("**Union Density by Treatment Status**"),
        subtitle = "In subset of parishes used in regression sample"
    ) %>%
    gtsave(here::here("figures", "092-tab-union-density-by-treatment-status.png"))


```



```{r}
df_union_density_wide_tab %>%
    ggplot(aes(x = year, y = union_density, color = treated)) +
    geom_line() 
```


