---
title: "Event study graph"
format: html
---

We want to make a plot of the share of electricity jobs (both direct and indirect) in the total number of jobs in the economy, over time. We will use the census data from 1890, 1900, 1910 and 1930.

## Trying again with new data.

What do we want to do? We want to make a plot of the share of electricity jobs (both direct and indirect) in the total number of jobs in the economy, over time. We will use the census data from 1890, 1900, 1910 and 1930.

```{r}
# install.packages("ipumsr")
library(ipumsr)
library(tidyverse)
library(gt)

# Example data
df_census_all <- read_ipums_micro("data/census/ipumsi_00010.xml")

df_census_all_clean_names <- df_census_all %>%
    janitor::clean_names()

df_census_short <- df_census_all_clean_names %>%
    # select the relevant columns
    select(year, contains("occ"), parse, bplse1, bplse2) %>%
    # remove labels to make files smaller
    zap_labels() %>%
    mutate(occstring = case_when(
        year == 1880 ~ se1880a_occstrng,
        year == 1890 ~ se1890a_occstrng,
        year == 1900 ~ se1900a_occstrng,
        year == 1910 ~ se1910a_occstrng,
        TRUE ~ "error"
    )) %>%
    select(-contains("se1")) %>%
    # tidy up occupational strings
    mutate(
        occstring = str_to_lower(occstring),
        occstring = str_squish(occstring)
    ) %>%
    # create a variable for direct electricity jobs
    mutate(electricity_job_direct = case_when(
        str_detect(occstring, "elektr") ~ 1,
        occstring == "elmontör" ~ 1,
        str_detect(occstring, "linjearbetare") ~ 1,
        str_detect(occstring, "kraftverksarbetare") ~ 1,
        TRUE ~ 0
    )) 

```

Here is the list of indirect electricity jobs, from Jakob's code:

```{r}
electricity_jobs_indirect_list <- c(
    "Maskinist",
    "Pappersbruksarbetare",
    "Verkstadsarbetare",
    "Metallarbetare",
    "Textilarbeterska",
    "Sömmerska s. e.",
    "Träarbetare",
    "Järnverksarbetare",
    "Montör",
    "Valsverksarbetare",
    "Sömmerska s.e.",
    "Bryggeriarbetare",
    "Gjuteriarbetare",
    "Rörverksarbetare",
    "Smidesarbetare",
    "Pappersfabriksarbetare",
    "Maskinarbetare",
    "Plåtslageriarbetare",
    "Filare",
    "Skofabriksarbetare",
    "Järnbruksarbetare",
    "Slakteriarbetare",
    "Svarvare",
    "Glasslipare",
    "Tegelarbetare",
    "Snickerifabriksarbetare",
    "Färgeriarbetare",
    "Järnsvarvare",
    "Mejeribiträde",
    "Sågverksarbetare",
    "Tegelfabriksarbetare",
    "Mejerist",
    "Fabriksarbeterska",
    "Smedsarbetare",
    "Träsliperiarbetare",
    "Filare",
    "Sågare",
    "Mekaniker",
    "Tändsticksfabriksarbetare",
    "Telefonarbetare",
    "Skoarbetare",
    "Metallarbetare",
    "Snickeriarbetare",
    "Trämassearbetare",
    "Maskinsnickare",
    "Pappersbruksarbetare",
    "Textilarbetare Vävare",
    "Smedmästare",
    "Textilarbetare väv.",
    "Spinnerska",
    "Gjuteriarbetare",
    "Möbelsnickeriarbetare",
    "Tillskärare",
    "Pressare",
    "Mekanisk verkstadsarbetare",
    "Tandtekniker",
    "Varvsarbetare",
    "Martinarbetare",
    "Textilfabriksarbetare",
    "Järnvägsverkstadsarbetare",
    "Valsverksarbetare vid järnbruk",
    "Fabriksarbetare",
    "Smed s. e.",
    "Maskinist",
    "Sulfitfabriksarbetare",
    "Verkstadsarbetare",
    "Montör",
    "Tändsticksfabriksarbeterska",
    "Plåtverksarbetare",
    "Kopparslagare",
    "Lådfabriksarbetare",
    "Textilfabriksarbetare",
    "Gjutare",
    "Pappersarbetare",
    "Smedslärling",
    "Bilmontör",
    "Ingenjör",
    "Fabrikör",
    "Spolerska",
    "Textilfabriksarbeterska",
    "Hyttarbetare",
    "Smältverksarbetare",
    "Möbelfabriksarbetare",
    "Svarvare",
    "Tobaksarbetare",
    "Tråddragare",
    "Smed",
    "Konfektionssömmerska",
    "Pressare",
    "Bageriarbetare",
    "Slöjdare",
    "Kartongarbetare",
    "Verkmästare",
    "Sulfitfabriksarbetare",
    "Modellsnickare",
    "Plåtslagare",
    "Spinnare",
    "Järnsvarvare",
    "Ritare",
    "Tändsticksfabriksarbetare",
    "Skofabriksarbetare",
    "Motorskötare",
    "Appretörarbetare",
    "Chokladarbetare",
    "Maskinarbetare",
    "Trikåfabriksarbetare",
    "Cellulosafabriksarbetare",
    "Slaktare s.e.",
    "Bleckslagare",
    "Sockerbruksarbetare",
    "Telefonreparatör",
    "Garvare",
    "Linnesömmerska",
    "Trämassefabriksarbetare",
    "Martins-arbetare vid järnbruk",
    "Spikfabriksarbetare",
    "Spinneriarbetare",
    "Smidesarbetare",
    "Svetsare",
    "Korsettarbetare",
    "Yllefabriksarbetare",
    "Masugnsarbetare",
    "Smörjare",
    "Cellulosafabriksarbetare ",
    "Tryckeriarbetare",
    "Slipmassefabriksarbetare",
    "Reparatör",
    "Tegelbruksarbetare",
    "Bryggeriarbetare",
    "Smedarbetare",
    "Mekanikerarbetare",
    "Glasverksarbetare",
    "Textilarbetare Väverska",
    "Pälssömmerska",
    "Kalkbruksarbetare",
    "Bleckslageriarbetare",
    "Polerare",
    "Sågverksägare",
    "Faktor",
    "Stålverksarbetare",
    "Textilarbetare Rullerska",
    "Jutefabriksarbeterska",
    "Verktygsarbetare",
    "Rullerska",
    "Armaturarbetare",
    "Cementfabriksarbetare",
    "Hyvlare",
    "Litografiarbeterska",
    "Sågarbetare",
    "Fräsare",
    "Textilarbetare väveri",
    "Sågmästare",
    "Fabrikssömmerska",
    "Tegelarbetare",
    "Sortererska vid pappersbruk",
    "Tricotstickerska",
    "Laboratoriebiträde",
    "Textilarbetare Spinnare",
    "Fabriksarbetare papp.",
    "Stickerska s.e.",
    "Hemsömmerska",
    "Maskinpassare vid pappersbruk",
    "Varvsarbetare",
    "Rördrageriarbetare vid järnbruk",
    "Plåtslageriarbetare",
    "Emaljarbetare",
    "Tvinnerska",
    "Sågverksförman",
    "Sömmerska s. e.",
    "Trikåarbetare",
    "Kaolinbruksarbetare",
    "Fanerfabriksarbetare",
    "Lådfabriksarbetare",
    "Textilarbetare Sömmerska",
    "Textilarbetare Spolerska",
    "Maskinstickerska",
    "Fabriksarbetare cellulosafabrik",
    "Trämassefabriksarbetare",
    "Ritare",
    "Typograflärling",
    "Kappsömmerska",
    "Sömmerska textil",
    "Jutefabriksarbetare",
    "Fabriksarbeterska",
    "Fabriksarbetare sulfatfabrik",
    "Fabriksarbeterska Väverska",
    "Möbelfabrikör",
    "Klensmed",
    "Maskinförare vid pappersbruk",
    "Plåtslageriarbetare M. V.",
    "Tillskärerska",
    "Maskinskötare",
    "Smidesmästare",
    "Margarinfabriksarbetare",
    "Gummifabriksarbetare",
    "Maskinförare",
    "Skomakeriarbetare",
    "Avsynare",
    "Läderarbetare",
    "Karamellfabriksarbetare",
    "Plåtarbetare",
    "Metallduksvävare",
    "Tråddrageriarbetare",
    "Sömmerska Hemmadotter",
    "Snickeriförman",
    "Kappfabrikssömmerska",
    "Borrare",
    "Tryckare",
    "Borrare",
    "Sömmerska s.e.",
    "Snickerifabrikör",
    "Svarvare Arbetare",
    "Valsare",
    "Mejerinna",
    "Smärglare",
    "Smältare",
    "Brädgårdsförman",
    "Kakelfabriksarbetare",
    "Varperska",
    "Konservfabriksarbetare",
    "Mekaniker",
    "Svetsare",
    "Gjutmästare",
    "Järnsvarvare M. V.",
    "Kopparslageriarbetare",
    "Maskinsnickeriarbetare",
    "Karamellarbetare",
    "Kranmaskinist ",
    "Maskinmästare",
    "Smedsdräng",
    "Textilarbetare",
    "Snickare vid möbelfabrik",
    "Torvströfabriksarbetare",
    "Smedmästare ag.",
    "Bilmontör",
    "Guldlistarbetare",
    "Västsömmerska",
    "Sågverksarbetare f.",
    "Underofficer Maskinist",
    "Tråddrageriarbetare vid järnbruk",
    "Fabrikssnickare",
    "Tekniskt biträde",
    "Fabriksarbetare vid Kallvalsverk",
    "Spårvagnskonduktör",
    "Smedsgesäll",
    "Väveriarbetare",
    "Borstbinderiarbetare",
    "Textilförman",
    "Verkstadsförman",
    "Bobinfabriksarbetare",
    "Cykelarbetare",
    "Sågställare",
    "Plyserska",
    "Linderska",
    "Plåtslagare vid mekanisk verkstad",
    "Väverska textilfabrik",
    "Sorterare",
    "Galvaniseringsarbetare",
    "Industriarbetare",
    "Tricotsömmerska",
    "Beredningsarbetare",
    "Kopparslagare",
    "Väverska",
    "Maskinsättare",
    "Väverska textil",
    "Syfabrikssömmerska",
    "Lokomotivförare",
    "Radiotelegrafist",
    "Tunnfabriksarbetare",
    "Linjearbetare",
    "Plåtslagare s. e.",
    "Sågägare",
    "Sågverksmaskinist",
    "Maskinmjölkare",
    "Kranförare",
    "Maskinformare",
    "Telefonföreståndare",
    "Plåtslagare s.e.",
    "Barkhusarbetare Pappersbruk",
    "Eldare vid pappersbruk",
    "Textilarbetare varp.",
    "Kullagerarbetare",
    "Gravör",
    "Kärnmakare",
    "Väverska s. e.",
    "Sliparbetare",
    "Glödgare",
    "Lokförare järnväg",
    "Radiomontör",
    "Linslagare",
    "Diversearbetare Pappersbruk",
    "Sockerfabriksarbetare",
    "Porslinsfabriksarbetare",
    "Sömmerska Skräddare",
    "Tobaksarbeterska",
    "Stålsynare vid järnbruk",
    "Chokladarbeterska",
    "Facitarbetare",
    "Stabbläggare",
    "Mejerska",
    "Stenarbetareänka",
    "Tricotarbetare",
    "Silverpolererska",
    "Mejeribiträde",
    "Träindustriarbetare",
    "Maskinarbetare vid snickerifabrik",
    "Tapetfabriksarbetare",
    "Stenkrossarbetare",
    "Kartongfabriksarbetare",
    "Brukstjänsteman",
    "Glaspackare",
    "Möbelfabrikssnickare",
    "Fabriksarbetare Ägare",
    "Järnarbetare mekanisk verkstad",
    "Verkstadsarbetare Filare",
    "Gummireparatör",
    "Textilarbeterska",
    "Diamantborrare",
    "Rorgängare",
    "Textilarbetare kamgarnspinneri",
    "Bänkarbetare",
    "Cellulosafabriksarbetare Diversearbetare",
    "Sockerbruksarbetare",
    "Gjutare M. V.",
    "Övermaskinist",
    "Spiksmed",
    "Fräsare",
    "Gummiarbetare",
    "Margarinarbetare",
    "Klädesfabriksarbetare",
    "Bleckslageriarbetare",
    "Textilarbetare Appretör",
    "Ackumulatorsfabriksarbetare",
    "Lastare",
    "Bergsingenjör",
    "Porslinsarbetare",
    "Spinnare textil",
    "Urmakare",
    "Rensare",
    "Konfektionsarbetare",
    "Smärglare",
    "Repslageriarbetare",
    "Sömmerska Konfektion",
    "Vävare yllefabrik",
    "Sömnadsarbetare",
    "Borstarbetare",
    "Lagersömmerska",
    "Verkstadsarbetare vid järnbruk",
    "Verkstadsarbetare vid järnbruk",
    "Träullfabriksarbetare",
    "Järnarbetare Pappersbruk",
    "Synerska",
    "Konfektionspressare",
    "Stålvägare vid järnbruk",
    "Sömnadsarbeterska",
    "Glasarbetare",
    "aaaa",
    "Spolerska textil",
    "Mekanikerarbetare",
    "Glasskärare",
    "Rullerska textil",
    "Mek. arbetare",
    "Sågare",
    "Maskinreparatör",
    "Gödningsfabriksarbetare",
    "Glasslipare",
    "Reparatör vid pappersbruk",
    "Vävare textilfabrik",
    "Plåtslageriarbetare v. mek. verkst.",
    "Silverpolererska",
    "Tvålfabriksarbetare",
    "Gårdfarihandlare",
    "Sömmerska fabrik",
    "Biografmaskinist",
    "Textilarbetare Spolare",
    "Sömnadsarbetare",
    "Martinsarbetare",
    "Manglerska",
    "Litograf",
    "Sågbladsarbetare vid järnbruk",
    "Textilarbetare Tvisterska",
    "Byxsömmerska",
    "Väverska yllefabrik",
    "Hattfabriksarbetare",
    "Dussinsömmerska",
    "Kragsömmerska",
    "Cellulosafabriksarbetare Reparatör",
    "Lagerbiträde textil",
    "Litografarbetare",
    "Filhuggare",
    "Rullare vid pappersbruk",
    "Skofabriksarbeterska",
    "Fabriksarbetare cellulosa",
    "Putsare Arbetare",
    "Kantsågare",
    "Galvanisör",
    "Ingeniör",
    "Elektriker Montör",
    "Bindgarnsarbetare",
    "Bruksarbetare Gjutare",
    "Lackerare",
    "Sömmerska duss.",
    "Sättare",
    "Sömmerskearbetare",
    "Mejerimaskinist",
    "Varvsplåtslagare",
    "Filhuggare",
    "Stålsynare",
    "Hyttarbetare Järnverk",
    "Makaroniarbetare",
    "Magasinarbetare",
    "Pappersbrukfabriksarbetare",
    "Väskfabriksarbetare",
    "Textilarbetare Varperska",
    "Marmeladarbeterska",
    "Klädsömmerska",
    "Textilsömmerska",
    "Fabriksarbetare vid järnbruk",
    "Torkare vid pappersbruk",
    "Spinnerska textilfabrik",
    "Sömmerska se.",
    "Fabriksförman",
    "Utearbetare vid sulfitfabrik",
    "Textilfabriksarbeterska",
    "Tillskärare",
    "Mjölkning",
    "Tyglagerska yllefabrik",
    "Stickerska textil",
    "Typograf Sättare",
    "Textilarbetare Färgare",
    "Sintringsarbetare",
    "Påsfabriksarbetare",
    "Järnarbetare Kockum",
    "Sömmerska trikåfabrik",
    "Färgeriarbetare textil",
    "Konfektionsfabrikssömmerska",
    "Fabriksarbetare pappersbruk",
    "Sågförman",
    "Grovarbetare vid järnbruk",
    "Förtennare",
    "Vaddfabriksarbetare",
    "Tricotstickare",
    "Pressare konfektion",
    "Cellulosafabriksarbetare",
    "Presserska",
    "Instrumentmakare",
    "Reparatör Pappersbruk",
    "Segelsömmare",
    "Sömmerska vid fabrik",
    "Fabriksarbetare Eldare",
    "Torvfabriksarbetare",
    "Bindgarnsarbeterska",
    "Styckmästare",
    "Civilingenjör",
    "Vävare textil",
    "Stenslipare",
    "Tillskärare konfektion",
    "Maskinmontör",
    "Textilarbetare Solverska",
    "Maskinist vid sågverk",
    "Motorförare",
    "Hjälpmontör",
    "Väverska Holm. br.",
    "Revolversvarvare",
    "Varvsförman",
    "Sömmerska vid fabrik",
    "Järnarbetare vid pappersbruk",
    "Fabriksarbetare Eldare",
    "Gjuteriarbetare M. V.",
    "Torvfabriksarbetare",
    "Spisbrödsfabriksarbetare",
    "Bindgarnsarbeterska",
    "Sågverksarbetare Diversearbetare",
    "Civilingenjör",
    "Cementgjuteriarbetare",
    "Vävare textil",
    "Tillskärare konfektion",
    "Verkstadsägare",
    "Maskinmontör",
    "Textilarbetare Solverska",
    "Verksarbetare",
    "Maskinist vid sågverk",
    "Bryggeriägare",
    "Martins-arbetare",
    "Vällare",
    "Vattenfabriksarbetare",
    "Glasarbetare Slipare",
    "Järnarbetare Filare",
    "Gjuterihantlangare",
    "Manufakturarbetare",
    "Mejslare",
    "Trävaruarbetare",
    "Typograf Tryckare",
    "Telefonstationsföreståndarinna",
    "Sömmerska herrkonfektion",
    "Maskinförman",
    "Mejerist Föreståndare",
    "Resårfabriksarbetare",
    "Dessinatör",
    "Kärnmakare Arbetare",
    "Smed vid stenhuggeri",
    "Grovarbetare Pappersbruk",
    "Brädgårdsarbetare Stabbläggare",
    "Maskinslipare",
    "Sågverksarbetare Lägenhetsägare",
    "Snickeriarbetare Möbel",
    "Fabriksarbetare Pappersbruk",
    "Förman Pappersbruk",
    "Tändsticksfabriksförman",
    "Verkstadsarbetare vid mekanisk verkstad",
    "Bleckvarufabriksarbetare",
    "Linnearbetare",
    "Skräddarearbetare",
    "Ciselör",
    "Textilarbetare Diversearbetare",
    "Mejerist",
    "Filare mekanisk verkstad",
    "Mekanisk verkstadslärling",
    "Verkstadsarbetare Plåtslagare",
    "Järnsvarvare vid stålpressningsverk",
    "Sågverksarbetare Smörjare",
    "Telefonväxelföreståndare",
    "Filare vid stålpressningsverk",
    "Fabriksarbetare Slipare",
    "Rullare å pappersbruk",
    "Maskinsnickare vid möbelfabrik",
    "Textilarbetare Tvinnerska",
    "Kullagerarbetare",
    "Knivsmed",
    "Fräsare Arbetare",
    "Järnarbetare Kockums",
    "Sömmerska Lägenhetsägare",
    "Linnesömmerska",
    "Filare Mekanisk verkstad",
    "Sågverksarbetare Eldare",
    "Textilarbetare Spinneri",
    "Smed Arbetare",
    "Stenarbetare vid stenindustri",
    "Kontorist textil",
    "Radiotelegrafist",
    "Järnvägsverkstadsförman",
    "Typograf Maskinsättare",
    "Mekaniker s. e.",
    "Gjutmästare",
    "Vågfabriksarbetare",
    "Rörläggningsarbetare",
    "Rörläggare Arbetare",
    "Kabelarbetare",
    "Knivarbetare",
    "Verkmästare vid pappersbruk",
    "Textilarbetare Smörjare",
    "Verkstadsarbetare Svarvare",
    "Järnarbetare vid mekanisk verkstad",
    "Sågverksarbetare Chaufför",
    "Textilarbetare Holm. br.",
    "Arbetare å Kalmar Bobin",
    "Svarvarbetare",
    "Virapassare Pappersbruk",
    "Klensmed vid järnbruk",
    "Hjälprullare Pappersbruk",
    "Mekanisk verkstadsarbetare",
    "Textilarbetare bom. väv.",
    "Valsarbetare",
    "Stärkelsefabriksarbetare",
    "Martinarbetare Järnverk",
    "Radiofabriksarbetare",
    "Toffelfabriksarbetare",
    "Maskinuppsättare",
    "Möbelsnickarearbetare",
    "Svarvare vid bobinfabrik",
    "Riktare",
    "Gelbgjutare",
    "Metalltryckare",
    "Fabriksarbetare Grovarbetare",
    "Linjeförman",
    "Sodabrännare vid pappersbruk",
    "Träullsfabriksarbetare",
    "Sågverksarbetare Kantare",
    "Verkmästare vid mekanisk verkstad",
    "Sågarbetare vid chokladfabrik",
    "Tråddragare järnbruk",
    "Slipare vid pappersbruk",
    "Cellulosafabriksarbetare Eldare",
    "Mekaniker s.e."
)
```

```{r}
electricity_jobs_indirect_list_tidy <- electricity_jobs_indirect_list %>%
    str_to_lower() %>%
    str_squish()

df_census_jobs <- df_census_short %>%
    mutate(electricity_job_indirect = sapply(occstring, function(x) {
        if (x %in% electricity_jobs_indirect_list_tidy) {
            return(1)
        } else {
            return(0)
        }
    }))

# df_census_jobs %>% write_rds("data/parishes/df_census_jobs_temp.rds")
```


Export list of 500 most common occupations that are not electricity jobs
```{r}
df_census_jobs %>%
    filter(electricity_job_direct == 0 & electricity_job_indirect == 0) %>%
    count(occstring, sort = TRUE) %>%
    head(500) %>%
    write_excel_csv("data/parishes/500_most_common_occupations_not_electricity_jobs.csv")
```

```{r}
# treated_parishes <- readxl::read_excel("data/parishes/treated_parishes.xlsx")

# treated_parishes <- treated_parishes %>%
#     select(parish_code, treated) %>%
#     distinct()

# df_census_jobs_treated <- df_census_jobs %>%
#     left_join(treated_parishes, by = c("bplse2" = "parish_code")) %>%
#     mutate(treated = case_when(
#         is.na(treated) ~ 0,
#         TRUE ~ treated
#     )) %>%
#     rename(birth_parish_treated = treated)

# df_census_jobs_treated %>%
#     select(year, electricity_job_direct, electricity_job_indirect, birth_parish_treated) %>%
#     count(year, electricity_job_indirect, birth_parish_treated)
```


```{r}
treated_and_control_parishes <- readxl::read_excel("data/parishes/treated_parishes_with_distance_threshold_and_population.xlsx")

treated_and_control_parishes_filtered <- treated_and_control_parishes %>%
    filter(distance_to_line <= 300,
    !is.na(population_1930)) %>% 
    mutate(parish_code = str_remove(parish_code, "SE/"),
    parish_code = as.numeric(parish_code)) %>%
    select(parish_code, treated) %>%
    distinct() 


df_census_jobs_treated_and_control <- df_census_jobs %>%
    left_join(treated_and_control_parishes_filtered, by = c("bplse2" = "parish_code")) %>%
    rename(birth_parish_treated = treated)


df_census_jobs_treated_and_control %>% count(birth_parish_treated)

df_census_jobs_treated_and_control_filtered <- df_census_jobs_treated_and_control %>%
    filter(!is.na(birth_parish_treated))
```


Count the kinds of jobs in 1910 that emerged in the data

```{r}
df_census_jobs_treated_and_control_filtered %>%
    filter(year == 1910) %>%
    filter(electricity_job_indirect == 1) %>%
    group_by(birth_parish_treated) %>%
    count(occstring, sort = TRUE) %>%
    slice_max(n, n = 10) %>%
    mutate(
        birth_parish_treated =
            case_when(
                birth_parish_treated == 0 ~ "Control Parishes",
                birth_parish_treated == 1 ~ "Early Access to Electricity Parishes"
            )
    ) %>%
    gt() %>%
    fmt_number(columns = vars(n), decimals = 0) %>%
    row_group_order(
        groups = c("Early Access to Electricity Parishes", "Control Parishes")
    ) %>%
    tab_style(
        style = cell_text(weight = "bold"),
        locations = cells_row_groups()
    ) %>%
    cols_label(occstring = "Occupation", n = "Count") %>%
    tab_header(
        title = "Top 10 Most Common Indirect Electricity-Related Jobs in 1910"
    ) %>% 
    gtsave("data/temp/top_indirect_electricity_jobs_1910.png")
```


Alternative approach

```{r}

# Calculate the proportions of electricity_job_direct for each year and birth_parish_treated group
proportion_df <- df_census_jobs_treated_and_control_filtered %>%
  group_by(year, birth_parish_treated) %>%
  summarise(
    n_total = n(),
    n_electricity = sum(electricity_job_direct),
    proportion = n_electricity / n_total
  )

# Reshape the data to have both groups on the same row
diff_df <- proportion_df %>%
  pivot_wider(
    names_from = birth_parish_treated,
    values_from = proportion,
    names_prefix = "proportion_"
  ) %>%
  mutate(difference = proportion_1 - proportion_0)

diff_df <- diff_df %>%
  mutate(
    proportion_0 = replace_na(proportion_0, 0),
    proportion_1 = replace_na(proportion_1, 0),
    difference = proportion_1 - proportion_0
  )
```


```{r}
library(dplyr)
library(tidyr)

# Step 1: Calculate the proportions of electricity_job_direct for each year and group
# Calculate the proportions of electricity_job_direct for each year and birth_parish_treated group
proportion_df <- df_census_jobs_treated_and_control_filtered %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity = sum(electricity_job_direct),
        proportion = n_electricity / n_total
    )

proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion, n_total) %>%
    pivot_wider(names_from = birth_parish_treated, values_from = c(proportion, n_total)) %>%
    mutate(difference = proportion_1 - proportion_0) %>%
    mutate(se_diff = sqrt(
        (proportion_0 * (1 - proportion_0) / n_total_0) +
            (proportion_1 * (1 - proportion_1) / n_total_1)
    ))


proportion_df %>%
    ggplot(aes(x = year, y = difference)) +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    labs(
        title = "Difference in Proportion of Direct Electricity Jobs",
        x = "Year",
        y = "Difference in Proportion (Treated - Untreated)"
    ) +
    theme_minimal() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.001))

```




```{r}
library(dplyr)
library(tidyr)

# Step 1: Calculate the proportions of electricity_job_direct for each year and group
# Calculate the proportions of electricity_job_direct for each year and birth_parish_treated group
proportion_df <- df_census_jobs_treated_and_control_filtered %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity = sum(electricity_job_indirect),
        proportion = n_electricity / n_total
    )

proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion, n_total) %>%
    pivot_wider(names_from = birth_parish_treated, values_from = c(proportion, n_total)) %>%
    mutate(difference = proportion_1 - proportion_0) %>%
    mutate(se_diff = sqrt(
        (proportion_0 * (1 - proportion_0) / n_total_0) +
            (proportion_1 * (1 - proportion_1) / n_total_1)
    ))


proportion_df %>%
    ggplot(aes(x = year, y = difference)) +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    labs(
        title = "Difference in Proportion of Direct Electricity Jobs",
        x = "Year",
        y = "Difference in Proportion (Treated - Untreated)"
    ) +
    theme_minimal() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) 

```


Combining into one graph

```{r}
library(dplyr)
library(tidyr)

# Step 1: Calculate the proportions of electricity_job_direct for each year and group
# Calculate the proportions of electricity_job_direct for each year and birth_parish_treated group
proportion_df <- df_census_jobs_treated_and_control_filtered %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity = sum(electricity_job_direct),
        proportion = n_electricity / n_total
    )

proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion, n_total) %>%
    pivot_wider(names_from = birth_parish_treated, values_from = c(proportion, n_total)) %>%
    mutate(difference = proportion_1 - proportion_0) %>%
    mutate(se_diff = sqrt(
        (proportion_0 * (1 - proportion_0) / n_total_0) +
            (proportion_1 * (1 - proportion_1) / n_total_1)
    ))


proportion_df_1 <- proportion_df %>%
    mutate(job_type = "Direct Electricity Jobs")


proportion_df <- df_census_jobs_treated_and_control_filtered %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity = sum(electricity_job_indirect),
        proportion = n_electricity / n_total
    )

proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion, n_total) %>%
    pivot_wider(names_from = birth_parish_treated, values_from = c(proportion, n_total)) %>%
    mutate(difference = proportion_1 - proportion_0) %>%
    mutate(se_diff = sqrt(
        (proportion_0 * (1 - proportion_0) / n_total_0) +
            (proportion_1 * (1 - proportion_1) / n_total_1)
    ))

proportion_df_2 <- proportion_df %>%
    mutate(job_type = "Indirect Electricity Jobs")


proportion_df <- rbind(proportion_df_1, proportion_df_2)

proportion_df %>%
    ggplot(aes(x = year, y = difference, colour = job_type)) +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff, colour = job_type), width = 0.2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    labs(
        title = "Difference in Proportion of Electricity Jobs",
        x = "Year",
        y = "Difference in Share of Electricity Jobs\nBetween Early Access to Electricity Parishes and Other Parishes",
        colour = "Job Type"
    ) +
    theme_minimal() +
    scale_colour_brewer(palette = "Dark2") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```







```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# Define a function to calculate proportions, differences, and plot
plot_difference_in_proportions <- function(data, job_type) {
    # Step 1: Calculate the proportions of the specified job type for each year and group
    proportion_df <- data %>%
        group_by(year, birth_parish_treated) %>%
        summarise(
            n_total = n(),
            n_electricity = sum({{ job_type }}), # Dynamically reference the job type variable
            proportion = n_electricity / n_total
        )

    # Step 2: Reshape the data and calculate the difference and standard error
    proportion_df <- proportion_df %>%
        pivot_wider(names_from = birth_parish_treated, values_from = proportion, names_prefix = "proportion_") %>%
        left_join(
            proportion_df %>% select(year, birth_parish_treated, n_total) %>%
                pivot_wider(names_from = birth_parish_treated, values_from = n_total, names_prefix = "n_total_"),
            by = "year"
        ) %>%
        mutate(difference = proportion_1 - proportion_0) %>%
        mutate(se_diff = sqrt(
            (proportion_0 * (1 - proportion_0) / n_total_0) +
                (proportion_1 * (1 - proportion_1) / n_total_1)
        ))

    # Step 3: Plot the results
    proportion_df %>%
        ggplot(aes(x = year, y = difference)) +
        geom_point() +
        geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
        labs(
            title = paste("Difference in Proportion of", job_type, "Jobs"),
            x = "Year",
            y = "Difference in Proportion (Treated - Untreated)"
        ) +
        theme_minimal()
}

# Example usage: Specify either "electricity_job_direct" or "electricity_job_indirect"
plot_difference_in_proportions(df_census_jobs_treated, "electricity_job_direct")

```


```{r}
df_census_jobs_treated %>%
    filter(electricity_job_direct == 1) %>%
    count(year, occstring, sort = T) %>%
    group_by(year) %>%
    slice_max(n = 10, order_by = n, with_ties = F) %>%
    gt() %>%
    tab_header(
        title = "Top direct electricity jobs",
        subtitle = "Number of jobs by year"
    ) %>%
    fmt_number(
        columns = vars(n),
        decimals = 0
    ) %>%
    tab_style(
        style = cell_text(weight = "bold"),
        locations = cells_row_groups()
    )  %>% 
    gtsave("data/temp/top_direct_electricity_jobs.png")
```


```{r}
df_census_jobs_treated %>%
    filter(electricity_job_indirect == 1) %>%
    count(year, occstring, sort = T) %>%
    group_by(year) %>%
    slice_max(n = 10, order_by = n, with_ties = F) %>%
    gt() %>%
    tab_header(
        title = "Top indirect electricity jobs",
        subtitle = "Number of jobs by year"
    ) %>%
    fmt_number(
        columns = vars(n),
        decimals = 0
    ) %>%
    tab_style(
        style = cell_text(weight = "bold"),
        locations = cells_row_groups()
    ) %>%
    cols_label(
        n = "Number of jobs",
        occstring = "Title"
    ) %>% 
        gtsave("data/temp/top_indirect_electricity_jobs.png")
```


Read in the 1930 data

```{r}
library(haven)

df_census_1930 <- read_dta("data/census/1930_census_regression_dataset_excl_unbalanced_controls.dta")

df_census_1930 %>%
    colnames()

df_census_1930_filtered <- df_census_1930 %>%
    select(electricity_job_direct, electricity_job_indirect, birth_parish_treated) %>%
    mutate(year = 1930)


df_census_jobs_treated_and_control_filtered_collected <- df_census_jobs_treated_and_control_filtered %>%
    select(year, birth_parish_treated, electricity_job_direct, electricity_job_indirect) %>%
    rbind(df_census_1930_filtered)




# Step 1: Calculate the proportions of electricity_job_direct for each year and group
# Calculate the proportions of electricity_job_direct for each year and birth_parish_treated group
proportion_df <- df_census_jobs_treated_and_control_filtered_collected %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity = sum(electricity_job_direct),
        proportion = n_electricity / n_total
    )

proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion, n_total) %>%
    pivot_wider(names_from = birth_parish_treated, values_from = c(proportion, n_total)) %>%
    mutate(difference = proportion_1 - proportion_0) %>%
    mutate(se_diff = sqrt(
        (proportion_0 * (1 - proportion_0) / n_total_0) +
            (proportion_1 * (1 - proportion_1) / n_total_1)
    ))


proportion_df %>%
    ggplot(aes(x = year, y = difference)) +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    labs(
        title = "Difference in Proportion of Direct Electricity Jobs",
        x = "Year",
        y = "Difference in Proportion (Treated - Untreated)"
    ) +
    theme_minimal() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.001))

```



Going long


```{r}
# Step 1: Calculate the proportions of electricity_job_direct for each year and group
# Calculate the proportions of electricity_job_indirect for each year and birth_parish_treated group
proportion_df <- df_census_jobs_treated_and_control_filtered_collected %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity = sum(electricity_job_indirect),
        proportion = n_electricity / n_total
    )

proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion, n_total) %>%
    pivot_wider(names_from = birth_parish_treated, values_from = c(proportion, n_total)) %>%
    mutate(difference = proportion_1 - proportion_0) %>%
    mutate(se_diff = sqrt(
        (proportion_0 * (1 - proportion_0) / n_total_0) +
            (proportion_1 * (1 - proportion_1) / n_total_1)
    ))


proportion_df %>%
    ggplot(aes(x = year, y = difference)) +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    labs(
        title = "Difference in Proportion of Direct Electricity Jobs",
        x = "Year",
        y = "Difference in Proportion (Treated - Untreated)"
    ) +
    theme_minimal() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.001))

```




```{r}
# Step 1: Calculate the proportions of electricity_job_direct and electricity_job_indirect for each year and group
proportion_df <- df_census_jobs_treated_and_control_filtered_collected %>%
    group_by(year, birth_parish_treated) %>%
    summarise(
        n_total = n(),
        n_electricity_indirect = sum(electricity_job_indirect),
        n_electricity_direct = sum(electricity_job_direct),
        proportion_indirect = n_electricity_indirect / n_total,
        proportion_direct = n_electricity_direct / n_total
    )

# Pivot wider to handle both direct and indirect calculations in one dataframe
proportion_df <- proportion_df %>%
    select(year, birth_parish_treated, proportion_indirect, proportion_direct, n_total) %>%
    pivot_wider(
        names_from = birth_parish_treated,
        values_from = c(proportion_indirect, proportion_direct, n_total)
    ) %>%
    mutate(
        difference_indirect = proportion_indirect_1 - proportion_indirect_0,
        difference_direct = proportion_direct_1 - proportion_direct_0,
        se_diff_indirect = sqrt(
            (proportion_indirect_0 * (1 - proportion_indirect_0) / n_total_0) +
                (proportion_indirect_1 * (1 - proportion_indirect_1) / n_total_1)
        ),
        se_diff_direct = sqrt(
            (proportion_direct_0 * (1 - proportion_direct_0) / n_total_0) +
                (proportion_direct_1 * (1 - proportion_direct_1) / n_total_1)
        )
    )




proportion_df %>%
    select(year, difference_indirect, difference_direct, se_diff_indirect, se_diff_direct) %>%
    pivot_longer(cols = -year) %>%
    mutate(group = str_extract(name, "indirect|direct")) %>%
    mutate(indicator = str_extract(name, "difference|se_diff")) %>%
    select(-name) %>%
    ungroup() %>%
    pivot_wider(names_from = indicator, values_from = value) %>%
    mutate(group = case_when(
        group == "indirect" ~ "Indirect Electricity Jobs",
        group == "direct" ~ "Direct Electricity Jobs"
    )) %>%
    ggplot(aes(x = year, y = difference, colour = group)) +
    geom_hline(yintercept = 0, linetype = 1, color = "black") +
    geom_vline(xintercept = 1909, linetype = "dashed") +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
    labs(
        # title = "Difference in Share of Electricity Related Jobs",
        x = "Year",
        y = "Difference in Share of Jobs \n(Early Access to Electricity - Other Parishes)",
        colour = "Job type",
        caption = "Note: dotted line indicates the year Olidan Power Station was built"
    ) +
    theme_minimal() +
    scale_colour_brewer(palette = "Dark2") +
    # facet_wrap(~group, scales = "free_y", nrow = 2) +
    theme(legend.position = "bottom") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.01))


```



Excluding 1910


```{r}
jpeg(here::here("figures", "event_study_excl_1910_same_y_axis.png"),
    width = 6, height = 6, units = "in", res = 300
)


proportion_df %>% 
    filter(year != 1910) %>%
    select(year, difference_indirect, difference_direct, se_diff_indirect, se_diff_direct) %>%
    pivot_longer(cols = -year) %>%
    mutate(group = str_extract(name, "indirect|direct")) %>%
    mutate(indicator = str_extract(name, "difference|se_diff")) %>%
    select(-name) %>%
    ungroup() %>%
    pivot_wider(names_from = indicator, values_from = value) %>%
    mutate(group = case_when(
        group == "indirect" ~ "Indirect Electricity Jobs",
        group == "direct" ~ "Direct Electricity Jobs"
    )) %>%
    ggplot(aes(x = year, y = difference, colour = group)) +
    geom_hline(yintercept = 0, linetype = 1, color = "black") +
    geom_vline(xintercept = 1909, linetype = "dashed") +
    geom_point() +
    geom_errorbar(aes(ymin = difference - 1.96 * se_diff, ymax = difference + 1.96 * se_diff), width = 0.2) +
    labs(
        # title = "Difference in Share of Electricity Related Jobs",
        x = "Year",
        y = "Difference in Share of Jobs \n(Early Access to Electricity - Other Parishes)",
        colour = "Job type",
        caption = "Note: dotted line indicates the year Olidan Power Station was built"
    ) +
    theme_minimal() +
    scale_colour_brewer(palette = "Dark2") +
    facet_wrap(~group,
        # scales = "free_y",
        nrow = 2
    ) +
    theme(legend.position = "bottom") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 0.01))

dev.off()
```